Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
removes extra 'still'
adds ionization limit comment to stromgren section

The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_{\rm J}$),  the solution is simply
%%%%%%%%%
\begin{eqnarray}
x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
%%%%%%%%%
The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0$, or $N_i = 1$) and dashed lines show that corresponding to $N_i=6$.
In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region.
Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.

The extent of ionized region may also be roughly estimated by Str\"omgren radius \citep{stromgren1939}: 
%%%%%%%%%
\begin{equation}
r_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
\end{equation}
%%%%%%%%%
which gives
%%%%%%%%%
\begin{eqnarray}
r_{\rm stromgren} \sim  
  \left\{
    \begin{array}{ll}
      67 ~R_J & \;\;\;(M_p = M_{\rm J}) \\
      310 ~R_J & \;\;\;(M_p = 10 M_{\rm J})
    \end{array}
  \right. \label{eq:stromgren}
\end{eqnarray}
%%%%%%%%%
for a planet around a red giants at 5~AU. 
The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}. Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small). 
The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.

>>>>

The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_{\rm J}$),  the solution is simply
%%%%%%%%%
\begin{eqnarray}
x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
%%%%%%%%%
The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0$, or $N_i = 1$) and dashed lines show that corresponding to $N_i=6$.
In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region.
Nevertheless, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.

The extent of ionized region may also be roughly estimated by Str\"omgren radius \citep{stromgren1939}: 
%%%%%%%%%
\begin{equation}
r_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
\end{equation}
%%%%%%%%%
which gives
%%%%%%%%%
\begin{eqnarray}
r_{\rm stromgren} \sim  
  \left\{
    \begin{array}{ll}
      67 ~R_J & \;\;\;(M_p = M_{\rm J}) \\
      310 ~R_J & \;\;\;(M_p = 10 M_{\rm J})
    \end{array}
  \right. \label{eq:stromgren}
\end{eqnarray}
%%%%%%%%%
for a planet around a red giants at 5~AU. 
The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}. Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citet{stromgren1939} is not small) on account of X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.
